A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Fix typo

\section{Conclusion and Future Work}
\label{section:conclusion}
This paper aims to proposes a highly decentralized, autonomous publish/subscribe model that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading. To clarify the data ownership and the identity verification, the data stream is stored on the Tangle, transmitted through MAM and automated by Ethereum smart contracts in our design. Compared to previous works, we (1) identify a trustless data trading infrastructure, (2) ensure the confidentiality of scalable IoT-based sensor data, and (3) consolidate the economic incentives in the entire ecosystem. Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticate the data providers to delegate the MAM operations to TAs, and conclude that the performance of the E2EE approach is more fitting than the MAM solution. In particular, this work discusses the refund mechanism for subscription-based IoT data trading: Launching, voting and implementing the refunding procedure.

However, this work has a main focus on the subscription-based model and relative experiment. Therefore, the next step is to extend the work to:
\begin{enumerate}
	\item reduce the use of Gas in key exchange process and consider the possibility of the zero-knowledge protocol to lower transaction costs
	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism
	\item develope a searching engine for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
\end{enumerate}

>>>>

\section{Conclusion and Future Work}
\label{section:conclusion}
This paper aims to propose a highly decentralized, autonomous publish/subscribe model that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading. To clarify the data ownership and the identity verification, the data stream is stored on the Tangle, transmitted through MAM and automated by Ethereum smart contracts in our design. Compared to previous works, we (1) identify a trustless data trading infrastructure, (2) ensure the confidentiality of scalable IoT-based sensor data, and (3) consolidate the economic incentives in the entire ecosystem. Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticate the data providers to delegate the MAM operations to TAs, and conclude that the performance of the E2EE approach is more fitting than the MAM solution. In particular, this work discusses the refund mechanism for subscription-based IoT data trading: Launching, voting and implementing the refunding procedure.

However, this work has a main focus on the subscription-based model and relative experiment. Therefore, the next step is to extend the work to:
\begin{enumerate}
	\item reduce the use of Gas in key exchange process and consider the possibility of the zero-knowledge protocol to lower transaction costs
	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism
	\item develop a searching engine for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
\end{enumerate}
